Plant occurrence subset by species with complete trait records

### 2024-09-05 code/L1/L1_P6_TropicalAndes_plant_occ.Rmd
update summary code

# Reshape to long format for easier plotting
combined_summary_long <- combined_summary %>%
  pivot_longer(cols = c(num_species, num_families, num_genera), 
               names_to = "category", 
               values_to = "count")
```

```{r}
ggplot(combined_summary_long, aes(x = source, y = count, fill = source)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Species, Genera, and Families",
       x = "Source",
       y = "Count",
       fill = "Source") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Angled x-axis labels
    plot.title = element_text(hjust = 0.5),             # Center the plot title
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10)
  ) +
  facet_wrap(~ category, scales = "free_y") +
  theme(strip.text.x = element_text(size = 12, face = "bold"))
ggsave("plant_taxonomic_coverage.png", plot = last_plot(), path = figure_path)
```

>>>>

# Reshape to long format for easier plotting
combined_summary_long <- combined_summary %>%
  pivot_longer(cols = c(num_species, num_families, num_genera), 
               names_to = "category", 
               values_to = "count")

# Reorder and rename the categories
combined_summary_long <- combined_summary_long %>%
  mutate(
    source = factor(source, levels = c("Data", "Checklist")),
    category = fct_recode(category,
                          "Species" = "num_species",
                          "Genera" = "num_genera",
                          "Families" = "num_families")
  )

# Reorder the category variable
combined_summary_long <- combined_summary_long %>%
  mutate(
    category = factor(category, levels = c("Species", "Genera", "Families"))
  )

# Custom colors for source
custom_colors <- c("Data" = "seagreen", "Checklist" = "darkgrey")
```

```{r}
ggplot(combined_summary_long, aes(x = source, y = count, fill = source)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Source",
       y = "Count",
       fill = "Source") +
  scale_fill_manual(values = custom_colors) + 
  theme_minimal() +
  theme(
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.position = "none"
  ) +
  facet_wrap(~ category, scales = "free_y") +
  theme(strip.text.x = element_text(size = 12, face = "bold"))
ggsave("plant_taxonomic_coverage.png", plot = last_plot(), path = figure_path)
```
